---
title: "P8105 Homework 1"
author: "Joshua Carpenter"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, results='hide', message=F}
library(moderndive)
library(hms)
library(ggplot2)
```


## Summary of Early January Weather Dataset
The `early_january_weather` (`r nrow(early_january_weather)` rows &#215; `r ncol(early_january_weather)` columns) dataset contains hourly meterological data for LGA, JFK and EWR for the month of January 2013. It has a structure of one row per timepoint per weather station (`origin`). We will be focused on the temperature (`temp`) in farenheit and relative humidity (`humid`) against time. The time of each measurement is recorded in the numeric variables `year`, `month`, `day`, and `hour`. The overall mean temperature in the dataset is `r mean(early_january_weather$temp) |> round(1)`&#8457; and the mean humidity is `r mean(early_january_weather$humid) |> round(1)`%.

Below is a plot of temperature against hour of the day (midnight to midnight). As we might expect, the temperature tends to reach a minimum in the early morning, increase during the day, and begin to drop off in the evening. The temperatures have a fairly narrow spread consistent with what we might expect in January, except for a couple of outlying days, which we can clearly follow - one very warm and two very cold. It would also appear that higher temperatures might be associated with higher humidities.

```{r}
ggplot(data = early_january_weather, 
       mapping = aes(x = hms(hours = hour), y = temp, color = humid)) +
  geom_point() +
  theme_bw() +
  coord_cartesian(
    ylim = c(0, max(early_january_weather$temp) + 5), 
    xlim = c(hms(minutes = -15), hms(hours = 23, minutes = 15)), 
    expand = FALSE) +
  labs(x = "Time of Day", 
       y = "Temperature", 
       color = "Humidity")
```

