---
title: "P8105 Homework 1"
author: "Joshua Carpenter"
date: "2023-09-22"
output: github_document
---

```{r setup, results='hide', message=F}
library(moderndive)
library(scales) # Used for time labels on plot in Q1
library(tidyverse)
```


## Question 1
The `early_january_weather` (`r nrow(early_january_weather)` rows &#215; `r ncol(early_january_weather)` columns) dataset contains hourly meterological data for LGA, JFK and EWR for the month of January 2013. It has a structure of one row per timepoint per weather station (`origin`). We will be focused on the temperature (`temp`) in fahrenheit and relative humidity (`humid`) against time. The time of each measurement is recorded in the numeric variables `year`, `month`, `day`, and `hour`. The overall mean temperature in the dataset is `r mean(early_january_weather$temp) |> round(1)`&#8457; and the mean humidity is `r mean(early_january_weather$humid) |> round(1)`%.

Below is a plot of temperature against time of the day (midnight to midnight). As we might expect, the temperature tends to reach a minimum in the early morning, increase during the day, and begin to drop off in the evening. The temperatures have a fairly narrow spread consistent with what we might expect in January, with a few particularly warm or cold days that we can clearly follow. It would also appear that higher temperatures might be associated with higher humidities.

```{r early_jan_temp}
ggplot(data = early_january_weather, 
       mapping = aes(x = hms::hms(hours = hour), y = temp, color = humid)) +
  geom_point() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  coord_cartesian(
    ylim = c(0, max(early_january_weather$temp) + 5), 
    xlim = c(hms::hms(minutes = -15), hms::hms(hours = 23, minutes = 59)), 
    expand = FALSE) +
  labs(x = "Time of Day", 
       y = "Temperature (\u00B0F)", 
       color = "Humidity") +
  scale_x_time(labels = label_time(format = "%H:%M")) +
  scale_color_continuous(labels = ~paste(.x, "%", sep = ""))
ggsave(filename = "early_jan_temp.jpg")
```


## Question 2
In this code chunk, we create a dataframe for the purposes of demonstrating the differences between variable types and what happens when you coerce one type into another. As we see from the warnings, the mean function produces NA for any vector that is not numeric or logical.
```{r var_types}
var_types_df <- tibble(
  norm = rnorm(10),
  gt0 = norm > 0,
  char = c(letters[1:8], "1", "34"),
  fact = factor(c("High", "Medium", "Medium", "Low", "High", "Low", 
                  "Low", "Low", "High", "Medium"), 
                c("Low", "Medium", "High"))
)
var_types_df |>
  summarise_all(mean)
```

If we coerce the character and factor variables into numeric, we could take the mean, but it might not be very meaningful.
```{r coersion, results='hide', message=F, warning=F}
var_types_df |>
  transmute(char_coer = as.numeric(char), fact_coer = as.numeric(fact)) |>
  summarise_all(mean, na.rm=T)
```


